Complexity Insights into Circular Economy

### 2016-11-17 paper.tex
.

\begin{abstract}

@@

\section*{General project description: CSSS 2016}
The 'circular economy' is recent approach on questions of sustainability. The current 'take, make, waste' way of producing is considered to be not sustainable anymore. Current thoughts on 'closing the loop' mechanisms on producing and consuming are booming in many different academic fields. However, not yet from an integrated point of view. The idea of 'closing the loop' mechanisms corresponds to complex system paradigms, however complexity science has hardly been utilized in this field. In this project we started brainstorming on how complexity science can contribute to the field of circular economy. We think there are many ways in which complexity science can contribute, both in methods and in theory.

%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

\subsection{Description of circular economy concept}

@@

%%%%%%%%%%%%%%%%%%%%%
\subsection{Prospective Literature review}

@@

\textit{This section gives a broad prospective literature review, not necessarily structured.}

@@

\subsection{Existing studies into circular economies}

@@

\subsection{Rational for our model/study}

@@

%%%%%%%%%%%%%%%%%%
\section{Model Description}

%%%%%%%%%%%%%%%%%%
\subsection{Model Core}

\paragraph{Model setup}

@@

\paragraph{Growing the circular economy network}

@@

\paragraph{Indicators of Circularity}

@@

%%%%%%%%%%%%%%%%%%
\subsection{Extensions}

@@

%%%%%%%%%%%%%%%%%%
\section{Results}

% TODO : when all line up, should be perfectly circular - sensitivity of moving slightly distribs.

% calibration on a given parc

@@

%%%%%%%%%%%%%%%%%%
\subsection{Implementation}

@@

%%%%%%%%%%%%%%%%%%
\subsection{Model Exploration}

%%%%%%%%%%%%%%%%%%
\subsubsection{Internal model validation}

@@

%%%%%%%%%%%%%%%%%%
\subsubsection{Uniform spatialization}

@@

%%%%%%%%%%%%%%%%%%
\subsubsection{Synthetic city system}

@@

%%%%%%%%%%%%%%%%%%
\subsubsection{Real city system}

@@

>>>>

\begin{abstract}
The 'circular economy' is recent approach on questions of sustainability. The current 'take, make, waste' way of producing is considered to be not sustainable anymore. Current thoughts on 'closing the loop' mechanisms on producing and consuming are booming in many different academic fields. However, not yet from an integrated point of view. The idea of 'closing the loop' mechanisms corresponds to complex system paradigms, however complexity science has hardly been utilized in this field. In this project we started brainstorming on how complexity science can contribute to the field of circular economy. We think there are many ways in which complexity science can contribute, both in methods and in theory.

@@

%%%%%%%%%%%%%%%%%%
\section*{Introduction}

@@

\subsection*{Towards a Circular Economy}

%%%%%%
% Concept description
%%%%%%

\subsubsection*{Concept}

@@

%%%%%%%%%%%%%%%%%%%%%
% Prospective Literature review 
%%%%%%%%%%%

@@

%\textit{This section gives a broad prospective literature review, not necessarily structured.}

\subsubsection*{Existing Works}

@@

%\subsection{Existing studies into circular economies}

% -> included in literature

@@

%%%%%%%%%%%%%%%
\subsection*{Models of Simulation to Assess Feasibility}

% Rational for our model/study : describe what we want to do, why and how

@@

%%%%%%%%%%%%%%%%%%
%\section{Model Description}
\section*{Methods} \label{sec:methods} % for scirep, standard sectioning

%%%%%%%%%%%%%%%%%%
\subsection*{Model Core}

%%%%%%%%%%%%%%%%%%
\subsubsection*{Model setup}

@@

%%%%%%%%%%%%%%%%%%
\subsubsection*{Growing the circular economy network}

@@

\subsubsection*{Indicators of Circularity}

@@

@@

%%%%%%%%%%%%%%%%%%
\section*{Results}

% TODO : when all line up, should be perfectly circular 
%  -> interesting to look at the sensitivity of circularity indicators when moving slightly distribs.

% calibration on a given parc ?

@@

%%%%%%%%%%%%%%%%%%
\subsection*{Implementation}

@@

%%%%%%%%%%%%%%%%%%
\subsection*{Model Exploration}

%%%%%%%%%%%%%%%%%%
\subsubsection*{Internal model validation}

@@

%%%%%%%%%%%%%%%%%%
\subsubsection*{Uniform spatialization}

@@

%%%%%%%%%%%%%%%%%%
\subsubsection*{Synthetic city system}

@@

%%%%%%%%%%%%%%%%%%
\subsubsection*{Real city system}

@@

%%%%%%%%%%%%%%%%
\section*{Discussion}

%%%%%%%%%%%%%%%%%%
\subsection*{Possible Extensions}
